\documentclass[letterpaper,17pt,twoside,extrafontsizes,final]{memoir}
\usepackage{fontspec}
\setmainfont{EBGaramond}

\begin{document}
\frontmatter
\title{English Missal}
\author{Michael Shirk}
\date{MMXIX}
\maketitle

\mainmatter
\chapter*{Mass}
\section*{While Vesting}

% 1662: The Form and Manner of Making, Ordaining, and Consecrating of Bishops, 
% Priests, and Deacons, According to the Order of The Church of England.
% Attributed to: Rabanus Maurus; Translator: John Cosin
{\itshape Veni Creator Spiritus}
{\obeylines
Come, Holy Ghost, our souls inspire, 
And lighten with celestial fire. 
Thou the anointing Spirit art, 
Who dost thy sevenfold gifts impart.

Thy blessed unction from above, 
Is comfort, life, and fire of love.
Enable with perpetual light 
The dulness of our blinded sight.

Anoint and cheer our soiled face 
With the abundance of thy grace. 
Keep far our foes, give peace at home; 
Where thou art guide, no ill can come.

Teach us to know the Father, Son, 
And thee, of both, to be but One; 
That, through the ages all along, 
This may be our endless song:

    Praise to thy eternal merit, 
    Father, Son, and Holy Spirit.
}
% Douay-Rheims Bible. Psalm 104:30
℣.\ Send forth thy Spirit, and they shall be created.
℟.\ And thou shalt renew the face of the earth. 

% 1662, The Order of the Administration of the Lord's Supper, or Holy Communion.
Almighty God, unto whom all hearts be open, all desires known, and from whom no secrets are hid; Cleanse the thoughts of our hearts by the inspiration of thy Holy Spirit, that we may perfectly love thee, and worthily magnify thy holy Name; through Christ our Lord. Amen.

\end{document}